\documentclass[a4paper,10pt]{article}
\usepackage[top=1.5cm, bottom=1.5cm, left=1.5cm, right=1.5cm]{geometry}

%-------------------- Formatting --------------------
\titleformat{\section}{\large\bfseries\color{black}}{}{0em}{}
\titlespacing*{\section}{0pt}{12pt}{4pt}
\setlist[itemize]{noitemsep, topsep=0pt, left=0pt}
\pagestyle{empty}

%-------------------- Begin Document --------------------
\begin{document}

\begin{center}
    {\LARGE \textbf{Selim Acerbas}} \\[4pt]
    \href{mailto:selimacerbas@gmail.com}{selimacerbas@gmail.com} $\vert$
    +41 798 388 613 $\vert$
    \href{https://linkedin.com/in/selim-acerbas-746a031ba}{linkedin.com/in/selim-acerbas} $\vert$
    \href{https://github.com/SelimAcerbas}{github.com/SelimAcerbas} \\
    Basel, Switzerland
\end{center}

\section*{Summary}
Systems Engineer with a strong background in cloud infrastructure, secure distributed systems, and automation. Hands-on experience developing machine learning pipelines, authentication systems, and scalable microservices. Specialized in Kubernetes, Go/Python, Terraform, and CI/CD. Passionate about abuse prevention, threat detection, and reliable infrastructure.

\section*{Technical Skills}
\textbf{Languages:} Go, Python, Rust, C++, Bash, Lua, JavaScript, Dart \\
\textbf{ML/AI:} TensorFlow (familiar), NLP, deep learning fundamentals, abuse signal design \\
\textbf{Cloud:} AWS, GCP, Azure, Kubernetes, Docker, Serverless (Lambda, Cloud Functions) \\
\textbf{Tools:} Terraform, ArgoCD, Prometheus, Istio, Cilium, Jenkins, GitHub Actions \\
\textbf{Security:} IAM, WAF, OIDC, OAuth, SAML, Gatekeeper, Kyverno

\section*{Experience}
\textbf{Systems Engineer}, Swisscom, Zurich \hfill \textit{Feb 2024 -- Present} \\
\vspace{-6pt}
\begin{itemize}
    \item Developed Kubernetes-native banking applications with a focus on secure container orchestration (Istio, ArgoCD).
    \item Built and maintained CI/CD pipelines for rapid and secure deployment of services.
    \item Integrated advanced authentication protocols (OIDC, OAuth, SAML) to harden system access.
    \item Contributed to fraud-resilient system design via network policies and security automation.
\end{itemize}

\textbf{DevOps Engineer}, Capgemini, Frankfurt \hfill \textit{Apr 2023 -- Feb 2024} \\
\vspace{-6pt}
\begin{itemize}
    \item Led deployment of serverless ML-based automation using GCP Cloud Functions, Pub/Sub, and Workflows.
    \item Engineered smart IoT microservices using AWS Lambda, API Gateway, and DynamoDB.
    \item Implemented machine learning signal pipelines for detecting access anomalies.
    \item Hands-on experience with abuse-prevention patterns in pharmacy data pipelines.
\end{itemize}

\textbf{Software Developer (Working Student)}, Fraunhofer IGD \hfill \textit{2021 -- 2022} \\
\vspace{-6pt}
\begin{itemize}
    \item Built sensor-integrated robot motion planning using C++ and Qt.
    \item Focused on safety-critical automation using microcontrollers and real-time signals.
\end{itemize}

\section*{Education}
\textbf{B.Sc. Electrical and Electronics Engineering}, Dokuz Eylul University \hfill \textit{2016 -- 2017} \\
\textbf{B.Sc. Electrical and Electronics Engineering}, Turkish Naval Academy \hfill \textit{2013 -- 2016}

\section*{Certifications}
\begin{itemize}
    \item HashiCorp Certified: Terraform Associate (2023--2025)
    \item AWS Certified Cloud Practitioner (2023--2026)
    \item ProgrammingExpert, SystemsExpert, AlgoExpert (ongoing)
\end{itemize}

\end{document}
